---
title: "First data visualisation with R"
description: |
  Last week, we learnt how to work with R Markdown document and some packages including tidyverse, ggplot and ggiraph for data visualisation. Today, we learnt the advantages of plotly over ggiraph.
author:
  - name: Nurulasyiqah Md. Taha
    url: https://www.linkedin.com/in/nurulasyiqah-md-taha/
date: 07-03-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

### How to install and launch R packages

The following code chunk installs and launches R packages.

```{r}
packages = c('DT', 'ggiraph',
              'plotly', 'tidyverse')
              
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

### How to import data

The following code chunk imports a .csv datafile. Ensure that the data file (and folder) is saved in the same location (working directory) as this R Markdown document.

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

### Comparing R Graphics and ggplot2
R Graphics:

* simpler code
* very simple visualisation

ggplot2:

* longer code
* highly customisable visualisation

### Layered grammar of graphics
These are the seven essential grammatical elements (first 3 elements are the foundation):

* Data
* Aesthetics *aes()* – How to we want to map visual att with various attributes of the data
* Geometrics *geom_()* – Visual elements such as point, bar, line, polygons, etc.
* Facets
* Statistics
* Coordinates
* Themes

### How to call the ggplot function
Use the *data argument* as an input to call the ggplot function

```{r}
ggplot(data = exam_data)
```

### How to use aes()
```{r}
ggplot(data = exam_data, aes(x = MATHS))
```

### How to use geom_bar()
```{r}
ggplot(data = exam_data, aes(x = RACE)) +
  geom_bar()
```


### How to use geom_dotplot()
```{r}
ggplot(data = exam_data, aes(x = MATHS)) +
  geom_dotplot(dotsize = 0.5)
```

<br> We make some refinement with the following changes to input arguments for geom_dotplot() and scale_y_continuous().

```{r}
ggplot(data = exam_data, aes(x = MATHS)) +
  geom_dotplot(binwidth=2.5,
               dotsize = 0.5) +
  scale_y_continuous(NULL,
                     breaks = NULL)
```

### How to separate the dotplot by race
Use the data argument "fill" in aes() as follows:

```{r}
ggplot(data = exam_data, 
       aes(x = MATHS,
        fill = RACE)) +
  geom_dotplot(binwidth=2.5,
               dotsize = 0.5) +
  scale_y_continuous(NULL,
                     breaks = NULL)
```

### How to define a different colour for entire graph
Use the data argument "fill" in geom_histogram() as follows:

```{r}
ggplot(data = exam_data, 
       aes(x = MATHS)) +
  geom_histogram(bins = 20,
                 color = "black", # border colour
                 fill = "light blue")
```

### How to create stacked barchart by gender
Use the data argument "fill" in aes() as follows:

```{r}
ggplot(data = exam_data, 
       aes(x = MATHS,
       fill = GENDER)) +
  geom_histogram(bins = 20,
                 color = "grey30")
```

Note the different impact on the graphs when data argument "fill" is used in aes() or geom_histogram().

### How plot different geom objects together

Note that the order of plotting the geom objects matters. Plot a geom object that covers an area first so that it does not "cover" subsequent geom objects.

```{r}
ggplot(data = exam_data, 
       aes(x = GENDER,
       y = MATHS)) +
  geom_boxplot() +
  geom_point(position = "jitter", 
             size = 0.5)
# jitter randomly distributes data points to have a sense of how sparse
```

### Interactive data visualisation - ggiraph methods
ggiraph supports three types of interactivity:

* Tooltip
* Onclick
* Data_id

Generally, no changes are required to the aesthetics created on the static graph using ggplot2. However, we need to change to geom_dotplot_interactive().

### How to create an interactive dotplot (tooltip)

```{r}
p <- ggplot(data = exam_data, aes(x = MATHS)) +
  geom_dotplot_interactive(aes(tooltip = ID),
                           stackgroups = TRUE,
                           binwidth = 1,
                           method = "histodot") +
  scale_y_continuous(NULL,
                     breaks = NULL)
girafe(
  ggobj = p,
  width_svg = 6,
  height_svg = 6*0.618
)
```


### How to create a hover effect with data_id aesthetic

On mouse hover on a student data point, the student's classmates will be highlighted.

```{r}
p <- ggplot(data = exam_data, aes(x = MATHS)) +
  geom_dotplot_interactive(aes(data_id = CLASS),
                           stackgroups = TRUE,
                           binwidth = 1,
                           method = "histodot") +
  scale_y_continuous(NULL,
                     breaks = NULL)
girafe(
  ggobj = p,
  width_svg = 6,
  height_svg = 6*0.618
)
```

We can combine data_id and tooltip as follows:

```{r}
p <- ggplot(data = exam_data, aes(x = MATHS)) +
  geom_dotplot_interactive(aes(data_id = CLASS,
                               tooltip = CLASS),
                           stackgroups = TRUE,
                           binwidth = 1,
                           method = "histodot") +
  scale_y_continuous(NULL,
                     breaks = NULL)
girafe(
  ggobj = p,
  width_svg = 6,
  height_svg = 6*0.618
)
```

### How to create a hyperlink

Web document link with a data object will be displayed on the web browser when clicked.

```{r}
exam_data$onclick <- sprintf("window.open(\"%s%s\")",
"https://www.moe.gov.sg/schoolfinder?journey=Primary%20school", as.character(exam_data$ID))
p <- ggplot(data = exam_data, aes(x = MATHS)) +
  geom_dotplot_interactive(aes(onclick = onclick),
                           stackgroups = TRUE,
                           binwidth = 1,
                           method = "histodot") +
  scale_y_continuous(NULL,
                     breaks = NULL)
girafe(
  ggobj = p,
  width_svg = 6,
  height_svg = 6*0.618)
```

### How to create interactive scatter plot using plot_ly()

The syntax of plot_ly() is similar to ggplot. Note the curly dash in front of the field name. For more information on working with different arguments of plotly, refer to [Plotly for R](https://plotly.com/r/).

```{r}
plot_ly(data = exam_data, 
            x = ~MATHS, 
            y = ~ENGLISH)
```

The immediate advantage of plotly is the mouse hover toolbar on top right-hand side of the plot:

* Download plot as png file
* Box and lasso selection
* Compare data on hover

### How to work with visual variable

For categorical data, different color for different categories. For numerical data, color will be on a gradient scheme.

```{r}
plot_ly(data = exam_data, 
            x = ~ENGLISH, 
            y = ~MATHS,
            color = ~RACE)
```

The legend is also interactive.

### How to change the colour palette

The following code chunk uses ColourBrewer:

```{r}
plot_ly(data = exam_data, 
            x = ~ENGLISH, 
            y = ~MATHS,
            color = ~RACE,
            colors = "Set1")
```


---

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.


