---
title: "First data visualisation with R"
description: |
  Last week, we learnt how to work with R Markdown document and some packages including tidyverse, ggplot and ggiraph for data visualisation. Today, we learnt the advantages of plotly over ggiraph.
author:
  - name: Nurulasyiqah Md. Taha
    url: https://www.linkedin.com/in/nurulasyiqah-md-taha/
date: 07-03-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

### How to install and launch R packages

The following code chunk installs and launches R packages.

```{r}
packages = c('DT', 'ggiraph',
              'plotly', 'tidyverse')
              
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

### How to import data

The following code chunk imports a .csv datafile. Ensure that the data file (and folder) is saved in the same location (working directory) as this R Markdown document.

```{r}
exam_data <- read_csv("data/Exam_data.csv")
```

### Comparing R Graphics and ggplot2
R Graphics:

* simpler code
* very simple visualisation

ggplot2:

* longer code
* highly customisable visualisation

### Layered grammar of graphics
These are the seven essential grammatical elements (first 3 elements are the foundation):

* Data
* Aesthetics *aes()* – How to we want to map visual att with various attributes of the data
* Geometrics *geom_()* – Visual elements such as point, bar, line, polygons, etc.
* Facets
* Statistics
* Coordinates
* Themes

### How to call the ggplot function
Use the *data argument* as an input to call the ggplot function

```{r}
ggplot(data = exam_data)
```

### How to use aes()
```{r}
ggplot(data = exam_data, aes(x = MATHS))
```

### How to use geom_bar()
```{r}
ggplot(data = exam_data, aes(x = RACE)) +
  geom_bar()
```


---

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.


