---
title: "Movement Visualisation with R"
description: |
  Today, we learnt how to visualise movement data using raster, sf, clock, tmap and tidyverse packages.
author:
  - name: Nurulasyiqah Md. Taha
    url: https://www.linkedin.com/in/nurulasyiqah-md-taha/
date: 07-03-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

### Install and launch raster, sf, clock, tmap and tidyverse packages of R

```{r}
packages = c('raster', 'sf', 'clock', 'tmap', 'tidyverse')
              
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

### How to import Raster file

Import the .tif file into an object, bgmap.

```{r}
bgmap <- raster("data/geospatial/MC2-tourist.tif")
bgmap
```

### How to create a map using tmap package

There are two modes of tmap - "plot" gives the static version, "view" gives the interactive version.

```{r}
tmap_mode("plot")
tm_shape(bgmap) +
  tm_raster(bgmap, legend.show = FALSE)
```

Note that the colors are awful because 'bgmap' layer is a three-band false colour image but tm_raster() only reads it as a single-band.

```{r}
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255)
```

### How to import vector GIS data file

```{r}
Abila_st <- st_read(dsn = "data/Geospatial", layer = "Abila")
```

We need to ensure the projection WGS 84 is the same.

### How to import gps data

```{r}
gps <- read_csv("data/aspatial/gps.csv")
glimpse(gps)
```

Note from the glimpse that:

* The timestamp is not in date-time format but in character format
* id field should be in factor data type

We use [clock package](https://www.tidyverse.org/blog/2021/03/clock-0-1-0/) to convert the timestamp format from character to m/d/Y H:M:S.

```{r}
gps$Timestamp <- date_time_parse(gps$Timestamp,
                zone = "",
                format = "%m/%d/%Y %H:%M:%S")
gps
```

```{r}
gps1 <- gps %>%
  filter(Timestamp < "2014-01-06 23:59:00")
```

To convert the ID field from numerical to character (factor) data type we use forcats package

```{r}
gps$id <- as_factor(gps$id)
```

### How to convert gps data into geometric simple feature data

```{r}
gps_sf <- st_as_sf(gps,
                   coords = c("long", "lat"),
                   crs = 4326)
gps_sf
```

### How to create movement path from GPS points

The code chunk below joins the GPS points into movement paths using the driver's ID as unique identifier.

```{r}
gps_path <- gps_sf %>%
  group_by(id) %>%
  summarise(m = mean(Timestamp),
            do_union = FALSE) %>%
  st_cast("LINESTRING") #To link the GPS points into a line
#mean is just to 'cheat' the group_by syntax

gps_path
```

### How to plot the GPS paths

```{r}
gps_path_selected <- gps_path %>%
  filter(id==1)
tmap_mode("view")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

The thicker lines shows that that route is taken multiple times.

---
Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.
