---
title: "Assignment"
description: |
  To use visual analytics to detect anomalies and suspicious behavior in movement and tracking data.
author:
  - name: Nurulasyiqah Md. Taha
    url: https://www.linkedin.com/in/nurulasyiqah-md-taha/
date: 07-13-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.retina=3,
                      echo = TRUE, 
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## 1. Introduction

[**VAST Challenge 2021 - The Kronos Incident (Mini-Challenge 2)**](https://vast-challenge.github.io/2021/index.html)

Between 20-21 Jan 2014, on the island country of Kronos, several employees of GAStech, a Tethys gas multinational, go missing.

To get to the bottom of this mystery, we will use visual analytic techniques to analyze data provided by GAStech to assist with law enforcement’s investigation and hopefully find the missing persons and bring them home safely. The data provided by GAStech covering the two weeks prior to the GAStech employees’ disappearance are as follows:

* GAStech employee’s credit card transactions and Kronos Kares loyalty card data, and
* Movement and tracking data from GAStech’s company cars which have GPS tracking.

## 2. Objective

The objective of this assignment is to use visual analytic techniques in purely R to surface and identify anomalies and suspicious behavior. 

## 3. Literature review

### 3.1 Previous work

Since VAST Challenge 2021 is a redux of [**VAST Challenge 2014**](http://visualdata.wustl.edu/varepository/VAST%20Challenge%202014/challenges/MC2%20-%20Patterns%20of%20Life%20Analysis/) with some variation, modified data and new questions, we reviewed past submissions for Mini-Challenge 2 for some inspiration on tackling this year's challenge.

We were particularly drawn to the following submissions:

* The [**DAC-MC2 team from Virginia Tech**](http://visualdata.wustl.edu/varepository/VAST%20Challenge%202014/challenges/MC2%20-%20Patterns%20of%20Life%20Analysis/entries/Virginia%20Tech) used a methodology called Points of Interest (**“POI”**) to identify POIs such as people’s homes, their work places, and recreational locations (e.g. restaurants, cafes). A location is considered a POI if the time spent at a location is more than 5 minutes and the location has a diameter of less than 50 meters. They then graphed the distribution of POI over time for various days (weekdays and weekends) and locations (i.e. home, work, recreation).

* Similarly, the [**MiddlesexMASS-Attfield-MC2 team from Middlesex University**](http://visualdata.wustl.edu/varepository/VAST%20Challenge%202014/challenges/MC2%20-%20Patterns%20of%20Life%20Analysis/entries/Middlesex%20University) used the Patterns of Life (**“POL”**) suite to create a map showing where each person was at any given time and for how long. They also overlayed credit card and loyalty transactions over their map.

* To better understand the credit card and loyalty card data, the [**IIITH-YASHASWI-MC2 team from the International Institute of Information Technology Hyderabad**](http://visualdata.wustl.edu/varepository/VAST%20Challenge%202014/challenges/MC2%20-%20Patterns%20of%20Life%20Analysis/entries/International%20Institute%20of%20Information%20Technology%20Hyderabad) visualized the distributions of credit card transactions by date and by person and employment title / employee title. This analysis enabled them to better understand typical patterns and identify transactions that deviated and stood out.

* The [**Purdue-Guo-MC2 team from Purdue University**](http://visualdata.wustl.edu/varepository/VAST%20Challenge%202014/challenges/MC2%20-%20Patterns%20of%20Life%20Analysis/entries/Purdue%20University) created a **Social Relationship Matrix**, which involves plotting a heatmap of the number of times GAStech employees meet each other over the course of the two weeks. The assumption is that the more frequent people meet, the closer relationship they have between them.

Eager to reproduce and improve the visualisations, we looked further into the dataset provided for the 2014 Challenge. While the datasets provided in 2014 were generally similar, we noted a significant difference in the 2021 datasets: Both the credit card transactions data and loyalty card transactions data do not reflect the name of the card holders.

This presents a further challenge for us to reproduce the inspiring visualisations above (especially the Social Relationship Matrix) and we have to consider alternatives or adaptations in some cases.

### 3.2 R Graph Gallery

We browsed the [R Graph Gallery](https://www.r-graph-gallery.com/index.html) for ideas on various types of charts and graphs that can be visualised using relevant R packages.

### 3.3 R packages

## 4. Data preparation

### 4.1 Data cleaning

**Install and launch R packages**

The following code chunk installs and launches the R packages we will use for data visualisation and analysis in this assignment.

```{r}
packages = c('DT', 'ggiraph', 'ggplot2', 'plotly', 
             'tidyverse', 'raster', 'sf', 'clock', 'tmap',
             'mapview', 'tidygraph', 'ggraph', 'visNetwork',
             'igraph', 'lubridate', 'clock')
              
for(p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```

**Import data files provided**

The following code chunk imports the four comma-separated values (.csv) data files provided for this Mini-Challenge - car-assignments.csv, cc_data.csv, gps.csv and loyalty_data.csv. The "data" folder containing the four data files is saved in the same location (working directory) as the R Markdown document to publish this webpage.

```{r}
car_assign<- read_csv("data/car-assignments.csv")
credit_card<- read_csv("data/cc_data.csv")
gps <- read_csv("data/gps.csv")
loyalty_card <- read_csv("data/loyalty_data.csv")
```

Take a glimpse of the "credit_card" dataset with the following code:

```{r}
glimpse(credit_card)
```

We need to change the "timestamp" column from character data type to date data type in m/d/Y H:M:S format and extract the "hour_of_day" and "day_of_week" for analysis later. We need to also change the "last4ccnum" column from numerical data type to character data type and rename it to "cc_id".

```{r}
credit_card$date <- date_time_parse(credit_card$timestamp,
                                             zone = "",
                                             format = "%m/%d/%Y")

credit_card$timestamp <- date_time_parse(credit_card$timestamp,
                                         zone = "",
                                         format = "%m/%d/%Y %H:%M")

credit_card$hour_of_day <- get_hour(credit_card$timestamp)

credit_card$day_of_week <- wday(credit_card$timestamp, label = TRUE, abbr = FALSE)

credit_card$last4ccnum <- as_factor(credit_card$last4ccnum)

credit_card <- credit_card %>%
  rename(cc_id = last4ccnum)

```

The cleaned version of "credit_card" dataset is as follows:

```{r}
glimpse(credit_card)
```

Next, we take a glimpse of the "loyalty_card" dataset with the following code:

```{r}
glimpse(loyalty_card)
```

We need to change the "timestamp" column from character data type to date data type in m/d/Y format and extract the "day_of_week" for analysis later.

```{r}
loyalty_card <- loyalty_card %>%
  mutate(timestamp = date_time_parse(timestamp,
                                     zone = "",
                                     format = "%m/%d/%Y")) %>%
  rename(date = timestamp)

loyalty_card$day_of_week <- wday(loyalty_card$date,
                               label = TRUE,
                               abbr = FALSE)
```

The cleaned version of "loyalty_card" dataset is as follows:

```{r}
glimpse(loyalty_card)
```

Next, we take a glimpse of the "gps" dataset with the following code:

```{r}
glimpse(gps)
```

We need to change the "Timestamp" column from character data type to date data type in m/d/Y H:M:S format and extract the "hour_of_day" and "day_of_week" for analysis later. We need to also change the "id" column from numerical data type to character data type and rename it to "CarID".

```{r}
gps$date <- date_time_parse(gps$Timestamp,
                            zone = "",
                            format = "%m/%d/%Y")

gps$Timestamp <- date_time_parse(gps$Timestamp,
                                 zone = "",
                                 format = "%m/%d/%Y %H:%M")

gps$hour_of_day <- get_hour(gps$Timestamp)

gps$day_of_week <- wday(gps$Timestamp, label = TRUE, abbr = FALSE)

gps$id <- as_factor(gps$id)

gps <- gps %>%
  rename(CarID = id)
```

The cleaned version of "gps" dataset is as follows:

```{r}
glimpse(gps)
```

Next, we take a glimpse of the "car_assign" dataset with the following code:

```{r}
glimpse(car_assign)
```

We need to also change the "CarID" column from numerical data type to character data type. We will also concatenate the "LastName" and "FirstName" of the employee into "EmployeeName".

```{r}
car_assign$CarID <- as_factor(car_assign$CarID)

car_assign <- car_assign %>%
  unite(EmployeeName, c("FirstName", "LastName"), sep = " ")
```

The cleaned version of "car_assign" dataset is as follows:

```{r}
glimpse(car_assign)
```
  
### 4.2 Geo-referencing

As the Abila, Kronos, tourist map image file provided (MC2-tourist.jpg) does not have coordinates projection, we need to perform geo-referencing. We used a geographic information system software, [QGIS](https://www.qgis.org/en/site/index.html), to geo-reference the image file with the Abila shapefile (in WGS84 coordinates) to obtain a geo-referenced tourist map (MC2-tourist.tif).

## 5. Visual analysis

### 5.1 Using just the credit and loyalty card data, identify the most popular locations, and when they are popular. What anomalies do you see? What corrections would you recommend to correct these anomalies?

When we first tried to run the code for the visualisation, we were prompted the following error message:

> invalid input 'Katerina’s Café' in 'utf8towcs'

Therefore, we ran the followings codes in the "credit_card" and "loyalty_card" datasets to resolve the accent characters.

```{r}
credit_card <- credit_card %>%
  mutate(location = ifelse(str_detect(location, "Katerina"), "Katerina's Cafe", location))

loyalty_card <- loyalty_card %>%
  mutate(location = ifelse(str_detect(location, "Katerina"), "Katerina's Cafe", location))
```

**Most popular locations based on credit card data**

```{r}
credit_card %>%
  mutate(location = fct_rev(fct_infreq(location))) %>%
  ggplot(aes(x = location)) +
  geom_bar(colour = "grey", fill = "dark blue") +
  xlab("Location") +
  ylab("No. of credit card transactions") +
  theme(axis.text.x = element_text(vjust = 0.5, hjust=1)) +
  coord_flip()
```

Based purely on the number of credit card transactions at each location over the course of two weeks, the top five popular locations were: 

1. Katerina's Cafe
2. Hippokampos
3. Guy's Gyros
4. Brew've Been Served
5. Hallowed Grounds

**Most popular locations based on loyalty card data**

```{r}
loyalty_card %>%
  mutate(location = fct_rev(fct_infreq(location))) %>%
  ggplot(aes(x = location)) +
  geom_bar(colour = "grey", fill = "dark green") +
  xlab("Location") +
  ylab("No. of loyalty card transactions") +
  theme(axis.text.x = element_text(vjust = 0.5, hjust=1)) +
  coord_flip()
```

Based purely on the number of loyalty card transactions at each location over the course of two weeks, the top five popular locations were: 

1. Katerina's Cafe
2. Hippokampos
3. Guy's Gyros
4. Brew've Been Served
5. Ouzeri Elian

**Most popular hours of the day based on credit card data**

```{r}
cc_hour_of_day <- credit_card %>%
  count(location, hour_of_day) %>%
  mutate(location = as.factor(location),
         hour_of_day = as.factor(hour_of_day),
         text = paste0("Location: ", location, "\n", 
                       "Hour of the day: ", hour_of_day, "\n", 
                       "Count: ", n))

hMap_hour_of_day <- ggplot(cc_hour_of_day, aes(hour_of_day,
                                             location,
                                             fill = n,
                                             text = text)) +
  geom_tile() +
  scale_fill_viridis(discrete = FALSE) +
  scale_y_discrete() +
  scale_x_discrete() +
    xlab("Hour of the day") +
  theme(panel.grid.major = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 5),
        axis.title.y = element_blank())

ggplotly(hMap_hour_of_day, tooltip = "text")

```

Brew've Been Served is a highly popular morning coffee place, as seen from the high number of transactions at between 7am and 9am. Dining at Katerina's Cafe for dinner appear to be very popular option, based on the high number of transactions between 8pm to 9pm.

During the two-week period of transactions, Daily Dealz recorded only 1 transaction at 6am, which is ironic for a place that suggests good deals on a daily basis. This piques our interest and we hope further investigation can reveal more information.

**Most popular days of the week based on credit card data**

```{r}
cc_day_of_week <- credit_card %>%
  count(location, day_of_week) %>%
  mutate(location = as.factor(location),
         day_of_week = as.factor(day_of_week),
         text = paste0("Location: ", location, "\n", 
                       "Day: ", day_of_week, "\n", 
                       "Count: ", n))

hMap_cc_day <- ggplot(cc_day_of_week, aes(day_of_week,
                                             location,
                                             fill = n,
                                             text = text)) +
  geom_tile() +
  scale_fill_viridis(discrete = FALSE) +
  scale_y_discrete() +
  scale_x_discrete() +
    xlab("Day of the week") +
  theme(panel.grid.major = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.y = element_blank())

ggplotly(hMap_cc_day, tooltip = "text")
```

**Most popular days of the week based on loyalty card data**

```{r}
lc_day_of_week <- loyalty_card %>%
  count(location, day_of_week) %>%
  mutate(location = as.factor(location),
         day_of_week = as.factor(day_of_week),
         text = paste0("Location: ", location, "\n", 
                       "Day: ", day_of_week, "\n", 
                       "Count: ", n))

hMap_lc_day <- ggplot(cc_day_of_week, aes(day_of_week,
                                             location,
                                             fill = n,
                                             text = text)) +
  geom_tile() +
  scale_fill_viridis(discrete = FALSE) +
  scale_y_discrete() +
  scale_x_discrete() +
    xlab("Day of the week") +
  theme(panel.grid.major = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.y = element_blank())

ggplotly(hMap_lc_day, tooltip = "text")
```

Credit card transactions and loyalty card transactions are aligned with each other throughout the week for both Katerina's Cafe and Brew've Been Served.


### 5.2 Add the vehicle data to your analysis of the credit and loyalty card data. How does your assessment of the anomalies in question 1 change based on this new data? What discrepancies between vehicle, credit, and loyalty card data do you find?

**Merging "car_assign" dataset with "gps" dataset**

As employees are assigned a car, we would merge the both data sets using left join to cater for trucks that would not be assigned to any employee.

```{r}
emp_gps <- gps %>%
  left_join(car_assign, by = c("CarID" = "CarID"))
```

The merged data set "emp_gps" is as follows:

```{r}
glimpse(emp_gps)
```

**Create a map of Abila, Kronos**

Import the raster file (MC2-tourist.tif) into an object, bgmap:

```{r}
bgmap <- raster("data/Geospatial/MC2-tourist.tif")
```

Run the following code to create a static map:

```{r}
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255)

```

Import vector GIS data file "Abila":

```{r}
Abila_st <- st_read(dsn = "data/Geospatial", layer = "Abila")
```

Convert the GPS data into geometric simple feature data:

```{r}
emp_gps_sf <- st_as_sf(emp_gps,
                   coords = c("long", "lat"),
                   crs = 4326)
```

**Create movement path from GPS points**

The following code chunk joins the GPS points into movement paths using the car ID as a unique identifier.

```{r}
gps_path <- emp_gps_sf %>%
  group_by(CarID) %>%
  summarise(m = mean(Timestamp),
            do_union = FALSE) %>%
  st_cast("LINESTRING")

gps_path
```

**Plotting GPS path of employee cars**

We should first check for any orphan lines (only 1 pair of coordinates cannot form a polyline path) and remove them.

```{r}
p = npts(gps_path, by_feature = TRUE)
gps_path2 <- cbind(gps_path, p)

gps_path_sort <- gps_path2 %>%
  arrange(p)
gps_path_sort
```

We observed that there is no car with orphan lines since there is no p = 1 in the gps_path_sort table above. We can therefore plot the paths for all Car IDs using the following code chunk:

**Route by Car ID 1 (assigned to Nix Calixto)**

```{r}
gps_path_selected <- gps_path %>%
  filter(CarID == 1) # Replace the CarID
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 2 (assigned to Lars Azada)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 2)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 3 (assigned to Felix Balas)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 3)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 4 (assigned to Ingrid Barranco)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 4)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Based on the thicker routes taken by Ingrid Barranco, she appears to visit the Desafio Golf Course quite often throughout the two weeks.

**Route by Car ID 5 (assigned to Isak Baza)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 5)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 6 (assigned to Linnea Bergen)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 6)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 7 (assigned to Elsa Orilla)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 7)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

The "steps-like" route taken Elsa Orilla suggests that she avoids taking the main roads as often as the smaller neighbourhood roads. She frequently visits the Chostus Hotel.

**Route by Car ID 8 (assigned to Lucas Alcazar)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 8)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 9 (assigned to Gustav Cazar)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 9)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

The GPS tracker on Car ID 9 was probably malfunctioning or tampered with, based on the stray lines on the map.

**Route by Car ID 10 (assigned to Ada Campo-Corrente)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 10)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 11 (assigned to Axel Calzas)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 11)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 12 (assigned to Hideki Cocinaro)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 12)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 13 (assigned to Inga Ferro)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 13)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Inga Ferro appears to take many alternative routes on a daily basis throughout the two weeks. We noticed that the car often stops or makes a u-turn at odd places off the main road, especially near to Pilau Street.

**Route by Car ID 14 (assigned to Lidelse Dedos)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 14)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Lidelse Dedos often visits the Chostus Hotel during the two weeks.

**Route by Car ID 15 (assigned to Loreto Bodrogi)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 15)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Loreto Bodrogi often visits the Chostus Hotel during the two weeks and drives a similar route to and from the Hotel as Lidelse Dedos. The car often stops or makes a u-turn at odd places off the main road, especially near to Pilau Street, similar to Inga Ferro.

**Route by Car ID 16 (assigned to Isia Vann)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 16)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Isia Vann often visits the Chostus Hotel during the two weeks and drives a similar route to and from the Hotel as Lidelse Dedos and Loreto Bodrogi.

**Route by Car ID 17 (assigned to Sven Flecha)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 17)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Sven Flecha often visits the Chostus Hotel during the two weeks and drives a similar route to and from the Hotel as Lidelse Dedos, Loreto Bodrogi and Isia Vann.

**Route by Car ID 18 (assigned to Birgitta Frente)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 18)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Birgitta Frente often visits the Chostus Hotel during the two weeks and drives a similar route to and from the Hotel as Lidelse Dedos, Loreto Bodrogi, Isia Vann and Sven Flecha.

**Route by Car ID 19 (assigned to Vira Frente)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 19)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Vira Frente often goes for long drives along Rist Way, to and fro the Chostus Hotel.

**Route by Car ID 20 (assigned to Stenig Fusil)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 20)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 21 (assigned to Hennie Osvaldo)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 21)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Hennie Osvaldo often visits the Chostus Hotel during the two weeks. The car often stops or makes a u-turn at odd places off the main road, especially near to Pilau Street, similar to Inga Ferro and Loreto Bodrogi.

**Route by Car ID 22 (assigned to Adra Nubarron)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 22)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 23 (assigned to Varja Lagos)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 23)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 24 (assigned to Minke Mies)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 24)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Minke Mies often visits the Chostus Hotel during the two weeks. The car often stops or makes a u-turn at odd places off the main road, especially near to Pilau Street, similar to Inga Ferro, Loreto Bodrogi and Hennie Osvaldo.

**Route by Car ID 25 (assigned to Kanon Herrero)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 25)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 26 (assigned to Marin Onda)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 26)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 27 (assigned to Kare Orilla)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 27)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 28 (assigned to Isande Borrasca)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 28)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

The GPS tracker on Car ID 28 was probably malfunctioning or tampered with, based on the odd lines on the map.

**Route by Car ID 29 (assigned to Bertrand Ovan)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 29)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

**Route by Car ID 30 (assigned to Felix Resumir)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 30)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Felix Resumir often visits the Chostus Hotel and Ahaggo Museum during the two weeks.

**Route by Car ID 31 (assigned to Sten Sanjorge Jr.)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 31)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Sten Sanjorge Jr., the President/CEO of GAStech, often visits the Desafio Golf Course and Chostus Hotel. 

**Route by Car ID 32 (assigned to Orhan Strum)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 32)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Orhan Strum, the SVP/COO of GAStech, often visits the Desafio Golf Course.

**Route by Car ID 33 (assigned to Brand Tempestad)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 33)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Brand Tempestad often visits the Chostus Hotel and Ahaggo Museum during the two weeks, similar to Felix Resumir.

**Route by Car ID 34 (assigned to Edvard Vann)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 34)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Edvard Vann often visits the Chostus Hotel and Ahaggo Museum during the two weeks, similar to Felix Resumir and Brand Tempestad.

**Route by Car ID 35 (assigned to Willem Vasco-Pais)**

```{r echo=FALSE}
gps_path_selected <- gps_path %>%
  filter(CarID == 35)
tmap_mode("plot")
tm_shape(bgmap) +
tm_rgb(bgmap, r = 1, g = 2, b = 3, alpha = NA, saturation = 1,
       interpolate = TRUE, max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()
```

Willem Vasco-Pais often visits the Desafio Golf Course and Chostus Hotel. 

```{r}


```

### 5.3 Can you infer the owners of each credit card and loyalty card? What is your evidence? Where are there uncertainties in your method? Where are there uncertainties in the data?

We may infer the owners of each credit card and loyalty card by plotting a network graph 

```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```

### 5.4 Given the data sources provided, identify potential informal or unofficial relationships among GASTech personnel. Provide evidence for these relationships.


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```

### 5.5 Do you see evidence of suspicious activity? Identify 1- 10 locations where you believe the suspicious activity is occurring, and why.


```{r}


```


```{r}


```


```{r}


```


```{r}


```


```{r}


```
